Outbreak response models of vaccine-preventable diseases in humans (1970-2019) - A systematic review

### 2023-06-21 analyses/scripts/orv_sys_rev_data_analysis.Rmd
Revised the YAML headers to be uniform

---
title: "Analysis of the included studies"
output:
  pdf_document:
    toc: yes
    keep_tex: yes
    fig_crop: no
---

>>>>

---
title: "Outbreak response models of vaccine-preventable diseases in humans (1970-2019) - A systematic review"
subtitle: "Supplementary file (analysis for main manuscript)"
author: "James M. Azam, Xiaoxi Pang, Elisha B. Are, Juliet R.C. Pulliam, Matthew J. Ferrari"
output:
  pdf_document:
    toc: yes
    fig_crop: no
---

### 2023-06-21 analyses/scripts/orv_sys_rev_supplementary.Rmd
Revised the YAML headers to be uniform

---
title: "Outbreak response models of vaccine-preventable diseases in humans (1970-2019) - A systematic review (Supplementary Files)"
author: "James Azam"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output:
  word_document:
    keep_md: yes
    toc: yes
---

>>>>

---
title: "Outbreak response models of vaccine-preventable diseases in humans (1970-2019) - A systematic review"
subtitle: "Supplementary file"
author: "James M. Azam, Xiaoxi Pang, Elisha B. Are, Juliet R.C. Pulliam, Matthew J. Ferrari"
output:
  pdf_document:
    toc: yes
    fig_crop: no
---
